Classless Java

### 2016-03-23 OOPSLA16/paper.tex
Move formalization to appendix.
Some edits and comments
Added missing appendix
Numeric citation style.
Some work in introduction
Content reorganization
Reviewd red H text, plus some fix to discussions
Changes
Polishing
Section 2
Some related work reorganization
Some reorganization, and some sad sacrifice to save some space
abstract

\documentclass[10pt,preprint]{sigplanconf}

@@

\usepackage{amsmath,amssymb}
\usepackage{balance,bbm,booktabs}
\usepackage{color}
\usepackage{etex}
\usepackage{fancyvrb}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{mathpartir,mathptmx,mdwlist,morefloats,multirow}
\usepackage{pstricks,pst-node,pst-tree,pgf}
\usepackage{rotating}
\usepackage{stmaryrd}
\usepackage{theorem}
\usepackage{url}
\usepackage{verbatim}
\usepackage{wrapfig}
\usepackage{xspace}

\usepackage[normalem]{ulem}
\usepackage[T1]{fontenc}
\usepackage[scaled=0.85]{beramono}
\usepackage{dirtree}

@@

\newcommand{\authornote}[3]{{\color{#2} {\sc #1}: #3}}
\newcommand\bruno[1]{\authornote{bruno}{red}{#1}}

@@

\title{Title Text}
\subtitle{Subtitle Text, if any}

\authorinfo{Name1}
           {Affiliation1}
           {Email1}
\authorinfo{Name2\and Name3}
           {Affiliation2/3}
           {Email2/3}

@@

\begin{abstract}
This is the text of the abstract.
\end{abstract}

\category{CR-number}{subcategory}{third-level}

@@

\keywords
keyword1, keyword2

@@

@@

\appendix
\section{Appendix Title}

This is the text of the appendix, if you need one.

\acks

Acknowledgments, if needed.

% We recommend abbrvnat bibliography style.

\bibliographystyle{abbrvnat}

@@

\begin{thebibliography}{}
\softraggedright

\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
P. Q. Smith, and X. Y. Jones. ...reference text...

\end{thebibliography}

>>>>

\documentclass[10pt,preprint,nocopyrightspace,numbers]{sigplanconf}

@@

\usepackage{listings}
\usepackage{multicol}
\usepackage{microtype}%if unwanted, comment out or use option "draft"
\usepackage[table,xcdraw]{xcolor}
\usepackage{color}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{stmaryrd}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage{url}
\usepackage{pstricks,pst-node,pst-tree}
\usepackage{bbm}
\usepackage{pgf}
\usepackage{multirow}

\usepackage{listings}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[normalem]{ulem}

\usepackage[T1]{fontenc}
\usepackage[scaled=0.85]{beramono}
\usepackage{mathpartir}
\usepackage{xspace}

\input{predef/def.tex}
\input{predef/java.tex}

@@

\newcommand{\authornote}[3]{{\color{#2} {\sc #1}: #3}}
\newcommand{\authorText}[2]{{\color{#1}#2}}
\newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
\newcommand\yanlin[1]{\authornote{yanlin}{purple}{#1}}
\newcommand\marco[1]{\authornote{marco}{blue}{#1}}
\newcommand\haoyuan[1]{\authornote{haoyuan}{cyan}{#1}}
\newcommand\brunoT[1]{\authorText{red}{#1}}
\newcommand\yanlinT[1]{\authorText{purple}{#1}}
\newcommand\marcoT[1]{\authorText{blue}{#1}}
\newcommand\haoyuanT[1]{\authorText{cyan}{#1}}

\newcommand\delete[1]{\textcolor{red}{\sout{#1}}}

\newcommand\sem[1]{\llbracket #1 \rrbracket_r}
\newcommand\sems[1]{\llbracket #1 \rrbracket_s}
\newcommand\tsem[1]{\llbracket #1 \rrbracket}
\newcommand{\rbm}[1]{\raisebox{-2.0ex}[0.5ex]{#1}}
\newcommand\nat[0]{\mathbb{N}}
\newcommand\unit[0]{\mathbbm{1}}

\newcommand\mixin{\mixinAnn\xspace}
%\renewcommand{\paragraph}[1]{\vspace{5pt}\noindent{\bf #1}}
\newenvironment{listing}{\vspace{-3pt}\begin{lstlisting}}{\end{lstlisting}\vspace{-3pt}}

%\theoremstyle{plain}
\newtheorem{thm}{Theorem}
\newtheorem{lem}{Lemma}
\newtheorem{thm2}{Theorem}
\newtheorem{lem2}{Lemma}

@@

\title{Classless Java}
\subtitle{Interface Based Programming for the Masses}

\authorinfo{}
           {}
           {}
%\authorinfo{Name2\and Name3}
%           {Affiliation2/3}
%           {Email2/3}

@@

\begin{abstract}

  This paper presents Interface Based (IB) object-oriented (OO)
  programming. Unlike class based OO programming, in IB programming there
  is no need for classes. To support state, IB programming does not
  use fields directly. Instead it uses \emph{abstract state
    operations}, such as getters, setters or clone-like methods. This
  new way to deal with state allows flexibility not typically
  available in CB languages.  In IB state (including mutable state)
  can be automatically type-refined in subtypes. The combination of a
  purely IB style of programming and automatic type-refinement enables
  powerful idioms using multiple inheritance and state.  To introduce
  IB to programmers we created Classless Java: an embeding of IB
  directly into Java. Classless Java uses annotation processing for
  code generation and relies on the new features of Java 8 for
  interfaces. We illustrate the usefulness of IB through various
  examples and case studies.

\end{abstract}

\begin{comment}
\category{CR-number}{subcategory}{third-level}

@@

\keywords
keyword1, keyword2
\end{comment}

@@

\input{sections/Overview.tex}

\input{sections/Implementation.tex}

@@

\input{sections/Translation.tex}

\input{sections/CaseStudy.tex}

\input{sections/FutureWork.tex}

\input{sections/RelatedWork.tex}

\input{sections/Conclusion.tex}

%\acks
%
% We recommend abbrvnat bibliography style.

\bibliographystyle{abbrvnat}
\bibliography{paper}

@@

%\begin{thebibliography}{}
%\softraggedright

%\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
%P. Q. Smith, and X. Y. Jones. ...reference text...

%\end{thebibliography}

\appendix
\input{sections/Appendix_Formalization.tex}
\input{sections/Appendix_Translation.tex}
\input{sections/Appendix.tex}
